Multispecies survey for diet comp

### 2020-11-30 SurveyDietCompTest.Rmd
apply dirichlet to diet, start taxonomic bias

@@

  alphavec <- alphamult *

  sampdiet <- DirichletReg::rdirichlet(1, alphavec)

>>>>

  # use grouptype column to allocate
  colnames(fgs) <- tolower(colnames(fgs))

  # check for GroupType or InvertType
  if (!("grouptype" | "inverttype") %in% colnames(fgs)) {
    stop(paste("The columns GroupType or InvertType ars not in your functional\n",
      "groups file."))
  }

  # change inverttype to grouptype, contents should be the same
  if("inverttype" %in% names(fgs)) names(fgs)[names(fgs) == 'inverttype'] <- 'grouptype'

  fgs$grouptype <- tolower(fgs$grouptype)

@@

	#tidy
	dietprop <- dat2 %>%
	  group_by(species, time.days, agecl) %>%
	  do(mutate(., dietSamp = DirichletReg::rdirichlet(1, alphamult * atoutput)))
